---
title: "AVM check"
author: "Peer Christensen"
date: "1/4/2019"
output:
  html_document:
    toc: yes
    code_folding: hide
    fig_width: 9
    fig_height: 10
  html_notebook:
    number_sections: yes
    code_folding: hide
    theme: cosmo
    fig_width: 9
    fig_height: 10
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=F,warning=F)
```

```{r}
library(tidyverse)
library(ggthemes)

theme_set(theme_light())

df <- read_csv("avm_check.csv") %>%
  mutate(houseNums = str_split(UNADR_NAME,",",2) %>% 
           map(1) %>% unlist() %>% parse_number() %>% 
           as.character(),
         House = ifelse(houseNums == "30", "target","other"))

df <- df %>% select_if(function(x) n_distinct(x) > 1)

df <- df %>% mutate_if(~n_distinct(.[]) <= 3, factor)

df <- df %>%
  select(-Kvhx,-KVH,-X,-Y, -Id,-Ejendomsnummer, -UNADR_PRIMUNIT_USAGE_CODE,
         -Right_UNADR_KVHX,PROP_VALUATION_AVM_DISC_NAME,-Sold_Property_Flag,
         -True_Performance_Flag,-ACADR_KEY,-CELL100_NAME,-PROP_KEY,-PROP_NO,-PROP_UNADR_KEY,
         -Right_UNADR_KVHX, -UNADR_NAME)

# check for large number of NAs
NAs <- df %>% group_by(houseNums) %>% apply(1, function(x) sum(is.na(x)))

df <- df %>% add_column(NAs)
```


# Quick summary

For one house (target) in this sample data set, the latest purchase price does not match the estimate provided by the AVM model.

Below, we see the data with the estimated m2 price and latest purchase price plotted against all relevant (and some irrelevant or of the wrong data type) numeric and categorical variables.

With respect to numeric variables, our target house looks like an outlier in terms of GrundVaerdi and MatrikeSamletAreal/UbebyggetGrundAreal.

Looking at the categorical variables, the target house is not associated with any rare classes.

Overall, when comparing the target to its nearest neighbours or identical x-axis values, the target is below average in terms of the m2 price estimate. Conversely, the target is above average for the latest purchase price.

# Numeric variables

## m2 Price estimate

```{r}
from <- seq(4,39,9)
to   <- seq(12,39,9)
batch = 1:length(from)

for (i in 1:length(from)) {
  
  p <- df %>%
    select_if(is.numeric) %>%
    select(-NAs,-BygningensAnvendelse) %>%
    add_column(House = df$House,houseNums = df$houseNums) %>%
    select(House,houseNums,EstimeretKvmPris,everything()) %>%
    select(c(1:3,from[i]:to[i])) %>%
    gather(variable, value,-House,-houseNums,-EstimeretKvmPris) %>%
    ggplot(aes(x=value,y=EstimeretKvmPris, colour = House)) +
    facet_wrap(~variable,scales="free",ncol=3) +
    geom_point(size=3, alpha = .8) +
    scale_color_tableau() +
    ggtitle(glue::glue("EstimeretKvmPris ~ Numeric variables: {batch[i]}")) +
    scale_y_continuous(labels = function(n) {
      trans = n / 1000
      paste0(trans, "K")
    })
  
  print(p)
}
```

## Last purchase price

```{r}
for (i in 1:length(from)) {
  
  p <- df %>%
    select_if(is.numeric) %>%
    select(-NAs,-BygningensAnvendelse) %>%
    add_column(House = df$House,houseNums = df$houseNums) %>%
    select(House,houseNums,SenesteHandelspris,everything()) %>%
    select(c(1:3,from[i]:to[i])) %>%
    gather(variable, value,-House,-houseNums,-SenesteHandelspris) %>%
    ggplot(aes(x=value,y=SenesteHandelspris, colour = House)) +
    facet_wrap(~variable,scales="free",ncol=3) +
    geom_point(size=3, alpha = .8) +
    scale_color_tableau() +
    ggtitle(glue::glue("SenesteHandelspris ~ Numeric variables: {batch[i]}")) +
    scale_y_continuous(labels = function(n) {
      trans = n / 1000000
      paste0(trans, "M")
    })
  
  print(p)
}
```

# Categorical variables

## m2 Price estimate

```{r}
from3  <- seq(4,30,9)
to3    <- seq(12,30,9)
batch3 <- 1:length(from3)

for (i in 1:length(from3)) {
  
  p <- df %>% 
    select_if(is.factor) %>%
    add_column(houseNums = df$houseNums, 
               EstimeretKvmPris = df$EstimeretKvmPris) %>% 
    select(House, houseNums, EstimeretKvmPris,everything(),-UNADR_PRIMUNIT_USAGE_NAME) %>%
    select(c(1:3,from3[i]:to3[i])) %>%
    gather(variable, value,-EstimeretKvmPris, -House,-houseNums) %>%
    ggplot(aes(x=value,y=EstimeretKvmPris)) +
    geom_boxplot(alpha = .7) +
    geom_jitter(aes(colour=House),alpha = .8, size = 3) +
    facet_wrap(~variable,scales="free") +
    scale_colour_tableau() +
    ggtitle(glue::glue("EstimeretKvmPris ~ Categorical variables: {batch3[i]}")) +
    scale_y_continuous(labels = function(n) {
      trans = n / 1000
      paste0(trans, "K")
    })
  
  print(p)
}
```

## Last purchase price

```{r}
for (i in 1:length(from3)) {
  
  p <- df %>% 
    select_if(is.factor) %>%
    add_column(houseNums = df$houseNums, 
               SenesteHandelspris = df$SenesteHandelspris) %>% 
    select(House, houseNums, SenesteHandelspris,everything(),-UNADR_PRIMUNIT_USAGE_NAME) %>%
    select(c(1:3,from3[i]:to3[i])) %>%
    gather(variable, value,-SenesteHandelspris, -House,-houseNums) %>%
    ggplot(aes(x=value,y=SenesteHandelspris)) +
    geom_boxplot(alpha = .7) +
    geom_jitter(aes(colour=House),alpha = .8,size = 3) +
    facet_wrap(~variable,scales="free") +
    scale_colour_tableau() +
    ggtitle(glue::glue("SenesteHandelspris ~ Categorical variables: {batch3[i]}")) +
    scale_y_continuous(labels = function(n) {
      trans = n / 1000000
      paste0(trans, "M")
    })
  
  print(p)
}
```
